Generating Random Logic Programs Using Constraint Programming

### 2020-05-15 text/paper2/bars.tex
Description of the experiments

% Created by tikzDevice version 0.12.3 on 2020-05-11 12:49:46
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 36.29) --
	( 97.08, 36.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 62.99) --
	( 97.08, 62.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 89.69) --
	( 97.08, 89.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 49.64) --
	( 97.08, 49.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 76.34) --
	( 97.08, 76.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,103.05) --
	( 97.08,103.05);

@@

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.97) -- ( 51.50, 75.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.90) -- ( 51.50, 71.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.07) -- ( 51.50, 74.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.99) -- ( 51.50, 71.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.47) -- ( 51.50, 84.39);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.39) -- ( 51.50, 80.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.71) -- ( 51.50, 79.64);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.64) -- ( 51.50, 75.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.44);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.44) -- ( 51.50, 73.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.96) -- ( 51.50, 75.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.88) -- ( 51.50, 71.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.19) -- ( 51.50, 74.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.50) -- ( 51.50, 74.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.42) -- ( 51.50, 70.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.45) -- ( 51.50, 78.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.37) -- ( 51.50, 74.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.07) -- ( 51.50, 77.99);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.99) -- ( 51.50, 74.07);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.86) -- ( 51.50, 76.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.78) -- ( 51.50, 72.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.26) -- ( 51.50, 75.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.18) -- ( 51.50, 71.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.53) -- ( 51.50, 75.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.46) -- ( 51.50, 71.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.17) -- ( 51.50, 78.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.09) -- ( 51.50, 74.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.05) -- ( 51.50, 75.98);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.98) -- ( 51.50, 72.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.59) -- ( 51.50, 74.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.51) -- ( 51.50, 70.59);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.60) -- ( 51.50, 75.53);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.53) -- ( 51.50, 71.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.73) -- ( 51.50, 75.65);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.65) -- ( 51.50, 71.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.27) -- ( 51.50, 75.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.19) -- ( 51.50, 71.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.86) -- ( 51.50, 74.79);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.79) -- ( 51.50, 70.86);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.78) -- ( 51.50, 76.70);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.70) -- ( 51.50, 72.78);

@@

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.27) -- ( 51.50, 74.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.19) -- ( 51.50, 70.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.09) -- ( 51.50, 79.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.01) -- ( 51.50, 75.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.26) -- ( 51.50, 78.18);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.18) -- ( 51.50, 74.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.92) -- ( 51.50, 75.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.84) -- ( 51.50, 71.92);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.89) -- ( 51.50, 74.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.82) -- ( 51.50, 70.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.81) -- ( 51.50, 74.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.73) -- ( 51.50, 70.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 71.32) -- ( 51.50, 75.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.24) -- ( 51.50, 71.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.51) -- ( 51.50, 77.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.43) -- ( 51.50, 73.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.68) -- ( 51.50, 76.60);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.60) -- ( 51.50, 72.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.68) -- ( 51.50, 79.61);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.61) -- ( 51.50, 75.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.08) -- ( 51.50, 74.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.01) -- ( 51.50, 70.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.32) -- ( 51.50, 76.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.24) -- ( 51.50, 72.32);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 70.44) -- ( 51.50, 74.37);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.37) -- ( 51.50, 70.44);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-14 17:55:45
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,130.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,130.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 36.97) --
	( 97.08, 36.97);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 64.98) --
	( 97.08, 64.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.71, 92.98) --
	( 97.08, 92.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 50.98) --
	( 97.08, 50.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71, 78.98) --
	( 97.08, 78.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.71,106.99) --
	( 97.08,106.99);

@@

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.50) -- ( 51.50, 78.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.42) -- ( 51.50, 74.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.55) -- ( 51.50, 77.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.47) -- ( 51.50, 73.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.41) -- ( 51.50, 87.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.33) -- ( 51.50, 83.41);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.42) -- ( 51.50, 82.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.34) -- ( 51.50, 78.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.11) -- ( 51.50, 80.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.03) -- ( 51.50, 76.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.48) -- ( 51.50, 78.40);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.40) -- ( 51.50, 74.48);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.90) -- ( 51.50, 80.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.82) -- ( 51.50, 76.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.95) -- ( 51.50, 76.87);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.87) -- ( 51.50, 72.95);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.09) -- ( 51.50, 81.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.02) -- ( 51.50, 77.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.69) -- ( 51.50, 80.62);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.62) -- ( 51.50, 76.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.42) -- ( 51.50, 79.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.34) -- ( 51.50, 75.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.74) -- ( 51.50, 77.67);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.67) -- ( 51.50, 73.74);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.03) -- ( 51.50, 77.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.96) -- ( 51.50, 74.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.80) -- ( 51.50, 80.72);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.72) -- ( 51.50, 76.80);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.58) -- ( 51.50, 78.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.50) -- ( 51.50, 74.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.04) -- ( 51.50, 76.96);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.96) -- ( 51.50, 73.04);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.11) -- ( 51.50, 78.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.03) -- ( 51.50, 74.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.24) -- ( 51.50, 78.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.16) -- ( 51.50, 74.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.75) -- ( 51.50, 77.68);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.68) -- ( 51.50, 73.75);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.33) -- ( 51.50, 77.25);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.25) -- ( 51.50, 73.33);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.34) -- ( 51.50, 79.26);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.26) -- ( 51.50, 75.34);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.66) -- ( 51.50, 79.58);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.58) -- ( 51.50, 75.66);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.71) -- ( 51.50, 76.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.63) -- ( 51.50, 72.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.76) -- ( 51.50, 81.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.69) -- ( 51.50, 77.76);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.89) -- ( 51.50, 80.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.82) -- ( 51.50, 76.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.43) -- ( 51.50, 78.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.36) -- ( 51.50, 74.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.36) -- ( 51.50, 77.29);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.29) -- ( 51.50, 73.36);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.28) -- ( 51.50, 77.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.20) -- ( 51.50, 73.28);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.81) -- ( 51.50, 77.73);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.73) -- ( 51.50, 73.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.10) -- ( 51.50, 80.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.03) -- ( 51.50, 76.10);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.24) -- ( 51.50, 79.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.16) -- ( 51.50, 75.24);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.38) -- ( 51.50, 82.31);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.31) -- ( 51.50, 78.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.51) -- ( 51.50, 76.43);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.43) -- ( 51.50, 72.51);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.85) -- ( 51.50, 78.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.78) -- ( 51.50, 74.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.89) -- ( 51.50, 76.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.82) -- ( 51.50, 72.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.54) -- ( 51.50, 77.46);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.46) -- ( 51.50, 73.54);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.88) -- ( 51.50, 83.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.81) -- ( 51.50, 79.88);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 88.89) -- ( 51.50, 92.81);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 92.81) -- ( 51.50, 88.89);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.05) -- ( 51.50, 76.97);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.97) -- ( 51.50, 73.05);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.11) -- ( 51.50, 77.03);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.03) -- ( 51.50, 73.11);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.17) -- ( 51.50, 77.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.09) -- ( 51.50, 73.17);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 72.85) -- ( 51.50, 76.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.77) -- ( 51.50, 72.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.27) -- ( 51.50, 84.20);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 84.20) -- ( 51.50, 80.27);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.55) -- ( 51.50, 87.47);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 87.47) -- ( 51.50, 83.55);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 90.50) -- ( 51.50, 94.42);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 94.42) -- ( 51.50, 90.50);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 76.52) -- ( 51.50, 80.45);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 80.45) -- ( 51.50, 76.52);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 75.93) -- ( 51.50, 79.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.85) -- ( 51.50, 75.93);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.09) -- ( 51.50, 77.02);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.02) -- ( 51.50, 73.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 73.21) -- ( 51.50, 77.13);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.13) -- ( 51.50, 73.21);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 77.77) -- ( 51.50, 81.69);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 81.69) -- ( 51.50, 77.77);

@@

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 90.09) -- ( 51.50, 94.01);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 94.01) -- ( 51.50, 90.09);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 74.16) -- ( 51.50, 78.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.08) -- ( 51.50, 74.16);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 79.84) -- ( 51.50, 83.77);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 83.77) -- ( 51.50, 79.84);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 78.15) -- ( 51.50, 82.08);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 82.08) -- ( 51.50, 78.15);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 93.27) -- ( 51.50, 97.19);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 47.58, 97.19) -- ( 51.50, 93.27);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 58.91) -- ( 49.54, 74.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.54, 48.64) -- ( 49.54, 34.20);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 38.40, 58.91) --
	( 38.40, 48.64) --
	( 60.68, 48.64) --
	( 60.68, 58.91) --
	( 38.40, 58.91) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.40, 53.42) -- ( 60.68, 53.42);
\definecolor{drawColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 84.78) -- ( 81.21, 88.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 88.71) -- ( 81.21, 84.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.38) -- ( 81.21, 89.30);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.30) -- ( 81.21, 85.38);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 81.90) -- ( 81.21, 85.82);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.82) -- ( 81.21, 81.90);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 85.85) -- ( 81.21, 89.78);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 89.78) -- ( 81.21, 85.85);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.71) -- ( 81.21, 87.63);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 87.63) -- ( 81.21, 83.71);

\path[draw=drawColor,draw opacity=0.25,line width= 0.4pt,line join=round,line cap=round] ( 77.29, 83.40) -- ( 81.21, 87.32);
